Soal Latihan

### 2021-10-20 Semester I/Analisis Numerik Lanjut/latihan/readme.Rmd
fixed equations

---
title: "Soal Latihan"
output: github_document
---

@@

```{r,echo=FALSE,fig.retina = 10,fig.align = "center"}
x = seq(0,1,by = 0.05)
f = function(x){(x-1)*tan(x) + x * sin(x*pi)}
y = f(x)

data.frame(x,y) %>%
  ggplot(aes(x,y)) +
  geom_line(color = "blue")

>>>>

---
title: "Soal Latihan"
output: 
  github_document:
    pandoc_args: --webtex
---

@@

```{r,echo=FALSE,fig.retina = 10,fig.align = "center"}
x = seq(0,1,by = 0.025)
f = function(x){(x-1)*tan(x) + x * sin(x*pi)}
y = f(x)

data.frame(x,y) %>%
  ggplot(aes(x,y)) +
  geom_line(color = "blue") +
  theme_minimal() +
  labs(title = "Fungsi f(x)")
